---
title: "9/29Lec"
author: "Yin Jiacheng"
date: "2024-09-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
isShow <- rnorm(1) > 0
```

# Why Git? Why GitHub?

## 1. Why Git?
Git is a version control system originally designed for collaborative software development. It manages a repository's evolution, akin to a powerful "Track Changes" feature. Data analysts have adapted Git to handle diverse project files, including data and reports. While solo users may find minimal benefits, the advantages become clear when collaborating with others.

## 2. Initial Setup Pain
Setting up Git requires installation and configuration, which can be a hassle. Users must establish a project directory, make it a Git repository, and adapt their workflow to include commits and pushes to GitHub. This initial discomfort is outweighed by long-term benefits.

## 3. Permissions Management
Public repositories are accessible to everyone, while private ones require permission settings for collaboration. GitHub also offers organizational features for team management.

## 4. GitHub Features
Notable features include:
- **Issues:** A bug tracker integrated with discussions and commit records.
- **Pull Requests:** Formal proposals for code changes that facilitate discussions and reviews.

## 5. R and GitHub
The R community actively uses GitHub for package development, with workflows that promote sharing R projects and reports effectively.

# Github account
Register a GitHub account (I assume that everyone has a GitHub account)

# RStudio
Install a pre-compiled binary of R for your OS from: https://cloud.r-project.org
However, your R version may not be the latest. You can check your R version by running the following code:
```{r eval=isshow}
R.version.string
#> [1] "R version 4.4.1 (2024-06-14)"
```
If your version is not higher than 4.4.1, you can run the following code:
```{r eval=isshow}
install.packages("installr")
require(installr)
updateR()
```
If you still can't update to the latest version, please install Rstudio again .





